---
title: "Assignment_12"
author: "Matthew Schultz"
date: '2023-03-31'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is my test example for an R markdown script

## This first code chunk will be used to install required packages.

For the sake of the assignment, I will keep the packages simple. Note that the `echo = TRUE` parameter was added to the code chunk to prevent to keep the packages listed in the html.

```{r, echo=TRUE}
library(tidyverse)
```

## I will now load the data set into R

The mtcars package is one of the most popular used data sets. It will be a good start for this test. Here is a [link](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) to a fleshed out explanation of the data set.

```{r}
cars <- mtcars

```

I will include a page break here

------------------------------------------------------------------------

Now I will want to include a few different plots.

### Scatter Plot measuring engine displacement and mpg

```{r}
ggplot(cars, aes(disp, mpg, color=factor(cyl))) +
  geom_jitter()
```

This plot does not have very descriptive headers to mark the data. For this we will need to include `labs(title = "Descriptive Title"`.

### Adding descriptive titles to ggplot graphs

```{r}
ggplot(cars, aes(disp, mpg, color=factor(cyl))) +
  geom_jitter() +
  labs(
    title = "Engine Displacement's affect on Miles per Gallon",
    subtitle = "Each point is colored by the number of cylinders."
  )
```

## Conclusion

Here is what we learned so far:

-   The impact of `echo` within an R code chunks
-   How to include links into the data set with `[text](link)`
-   How to include inline pieces of code with double \`
-   How to include list with \*
-   That pound signs con produce different heading for the script
